
% "SAMMELBAND" EXAMPLE setup



@BOOK{Hogg:ITM,
  AUTHOR       = "Hogg, R. V., McKean, J. W., & Craig, A. T",
  TITLE        = "{Introduction to Mathematical Statistics.}",
  SERIES       = {"None"},
  PUBLISHER    = "Pearson",
  YEAR         = "2019",
  ADDRESS      = "Boston"
}

@BOOK{Illo-D:IStat,
  AUTHOR       = "Illowsky, B., & Dean, S.,",
  TITLE        = "{Introductory statistics.}",
  SERIES       = {"None"},
  PUBLISHER    = "OpenStax",
  YEAR         = "2020",
  ADDRESS      = "https://openstax.org/details/introductory-statistics"
}

@BOOK{Liu:PAB,
  AUTHOR       = "Liu, Y., & Abeyratne, A. I.",
  TITLE        = "{Practical applications of Bayesian reliability.}",
  SERIES       = {"None"},
  PUBLISHER    = "Wiley",
  YEAR         = "2019",
  ADDRESS      = "Cornwall, Great Britain"
}

@BOOK{Richy:AIM,
  AUTHOR       = "Richard J. Larsen and Morris L. Marx",
  TITLE        = "{An Introduction to Mathetical Statistics and Its Applications.}",
  SERIES       = "{6th edition}",
  PUBLISHER    = "Pearson",
  YEAR         = "2018",
  ADDRESS      = "Boston"
}


@BOOK{Tilman:RBK,
  AUTHOR       = "Tilman M. Davies",
  TITLE        = "{The Book of R: A First Course In Programing and Statistics.}",
  SERIES       = {"None"},
  PUBLISHER    = "No Starch Press, Inc.",
  YEAR         = "2016",
  ADDRESS      = "San Francisco"
}


@Misc{Wolfram_Alpha,
  author = "{Wolfram Inc.}",
  title = "{Wolfram | Alpha}",
  year = "2021",
  note = "(URL: \url{https://wolframalpha.com} [last access 10.06.2021])"
  }

@INCOLLECTION{sammelband,
  AUTHOR       = "Peter Müller and Max Mustermann",
  TITLE        = "{Artikel in Sammelband}",
  SERIES       = {2. Auflage},
  NOTE         = "{(Hrsg.: Sammelband für IUBH.)}",
  PUBLISHER    = "Rheinwerk Verlag",
  YEAR         = "2019",
  ADDRESS      = "Bonn",
  PAGES        = "{S. 9-22}"
}

% JOURNAL ARTICLE EXAMPLE setup
@ARTICLE{article1,
  AUTHOR       = "Schülers",
  YEAR         = "2021",
  TITLE        = "{Zeitschriftenartikel}",
  NOTE         = "{In: Frankfurter Allgemeine Zeitung}",
  VOLUME       = "10.",
  SERIES       = "{Heft 20}",
  PAGES        = "{S. 10 - 14}"
}


%https://www.oxfordmartin.ox.ac.uk/downloads/academic/The_Future_of_Employment.pdf
@MISC{DueckKo:2016,
  AUTHOR       = "Gunter Dueck",
  TITLE        = "{Zwischen industralisierendem Downgrade und notwendigem Upgrade/Empowerment}",
  YEAR 		   = "2016",
  NOTE         = "(auf dem AKAC-Kongress)."
}
@MISC{Gray:2016,
  AUTHOR       = "Alex Gray",
  TITLE        = "The 10 skills you need to thrive in the Fourth Industrial Revolution",
  YEAR 		   = "2016",
  NOTE         = "(URL: \url{https://www.weforum.org/agenda/2016/01/the-10-skills-you-need-to-thrive-in-the-fourth-industrial-revolution/} [letzter Zugriff: 08.08.2018])."
}
%https://www.weforum.org/agenda/2016/01/the-10-skills-you-need-to-thrive-in-the-fourth-industrial-revolution/
@MISC{Gage:18,
  AUTHOR       = "Justin Gage",
  TITLE        = "{Introduction to Microservices}",
  YEAR 		   = "2018",
  NOTE         = "(URL: \url{https://blog.algorithmia.com/introduction-to-microservices/} [last access: 02.06.2019])."
}
%https://blog.algorithmia.com/introduction-to-microservices/


@BOOK{Richy:AIM,
  AUTHOR       = {Richard J. Larsen and Morris L. Marx},
  TITLE        = {An Introduction to Mathetical Statistics and Its Applications.},
  SERIES       = {6th edition},
  PUBLISHER    = {Pearson},
  YEAR         = {2018},
  ADDRESS      = {Boston},
}


@BOOK{Tilman:RBK,
  AUTHOR       = {Tilman M. Davies},
  TITLE        = {The Book of R: A First Course In Programing and Statistics.},
  SERIES       = {None},
  PUBLISHER    = {No Starch Press, Inc.},
  YEAR         = {2016},
  ADDRESS      = {San Francisco},
}


@Misc{Wolfram_Alpha,
  author = {Wolfram Inc.},
  title = {Wolfram | Alpha},
  year = {2021},
             % note = (URL: \url{https://wolframalpha.com} [last access 10.06.2021]),
  
}
  
 % https://www.wolframalpha.com/input/?i2d=true&i=Divide%5B1%2C2%CF%80%5DIntegrate%5BSqrt%5BPower%5Bx%2C2%5D%2BPower%5By%2C2%5D%5D%2C%7Bx%2C0%2C2%CF%80%7D%2C%7By%2C0%2C1%7D%5D
